Actuator line modeling of vertical-axis turbines

### 2018-04-08 paper.tex
Remove comma from superscript
Update case file citations

% Authors, for the paper (add full first names)
\Author{
    Peter Bachant $^{1}$\orcidA{},
    Anders Goude $^{2,}$
    and Martin Wosnik $^{1,}$*
}

@@

Similar numerical settings were used for each turbine as well. The Sheng et al.
DS model was used with the default coefficients given in \cite{Sheng2008}, and
the Goude flow curvature correction was employed. A second order backward
difference was used for advancing the simulation in time, and second order
linear schemes were used for the majority of the terms' spatial discretizations.
The only major difference between the two simulation configurations was that the
end effects model was deactivated for the RM2, since it reduced $C_P$ far below
the experimental measurements. This modification is consistent with the RM2
blades' higher aspect ratio (15 versus the UNH-RVAT's 7.1) and tapered planform,
though will need to be investigated further. The number of elements per actuator
line was set to be approximately equal to the total span divided by the Gaussian
force projection width $\epsilon$. Case files for running all the simulations
presented here with OpenFOAM 3.0.x are available from
\cite{Bachant2016-UNH-RVAT-turbinesFoam-v1.0.0,
Bachant2016-RM2-turbinesFoam-v1.0.0,
Bachant2016-UNH-RVAT-turbinesFoam-v1.0.0-LES}.

>>>>

% Authors, for the paper (add full first names)
\Author{
    Peter Bachant $^{1}$\orcidA{},
    Anders Goude $^{2}$
    and Martin Wosnik $^{1,}$*
}

@@

Similar numerical settings were used for each turbine as well. The Sheng et al.
DS model was used with the default coefficients given in \cite{Sheng2008}, and
the Goude flow curvature correction was employed. A second order backward
difference was used for advancing the simulation in time, and second order
linear schemes were used for the majority of the terms' spatial discretizations.
The only major difference between the two simulation configurations was that the
end effects model was deactivated for the RM2, since it reduced $C_P$ far below
the experimental measurements. This modification is consistent with the RM2
blades' higher aspect ratio (15 versus the UNH-RVAT's 7.1) and tapered planform,
though will need to be investigated further. The number of elements per actuator
line was set to be approximately equal to the total span divided by the Gaussian
force projection width $\epsilon$. Case files for running all the simulations
presented here with OpenFOAM v5.0 are available from
\cite{Bachant2018-UNH-RVAT-turbinesFoam-v1.1.0,
Bachant2018-RM2-turbinesFoam-v1.1.0}.
